The pollination trade-off

### 2018-09-19 paper/manuscript.Rmd
Remove figure pollen density from supplementary.
Not necessary as the second figure takes care of the whole deal

Each model set was based on the same one hundred bootstrap resamples of the deposition data. 
We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
In each data replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-log-transformed-or-not) and \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure. 
Finally, for the models of the relative amounts of pollen we calculated the difference between the pollen density among treatments.

>>>>

Each model set was based on the same one hundred bootstrap resamples of the deposition data. 
We used bootstrap resampling because, as open and bagged flowers were not paired, this allowed us to directly model the *gain* in pollen density rather than density itself. 
In each data replicate we randomly sampled with replacement a number of open flowers within each community-species combination and an equal number of closed flowers. 
We then log-transformed the pollen densities to improve normality and minimise the impact of outliers (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)), this generally offered better results that a generalised linear model with poisson (or quasiposson) error structure. 
Finally, for the models of the relative amounts of pollen we calculated the difference between the pollen density among treatments.

### 2018-09-19 paper/supp-info.Rmd
Remove figure pollen density from supplementary.
Not necessary as the second figure takes care of the whole deal

```{r fig-deposition-logtransformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown)."}
drake::loadd(fig_pollen_density)

>>>>

```{r fig-deposition-log-transformed-or-not, fig.height = 2, fig.cap = "Distribution of stigmatic pollen density plotted in (A) a linear scale, and (B) a logarithmic scale (zero values not shown).", eval=F}
drake::loadd(fig_pollen_density)
